### 2025-05-23 conclusions.tex
More fixes eliminating some unnecessary "fake" math formulas

To the best of our knowledge, this is the first mechanised proof of CLT beyond the I.I.D.~cases.
This version, usually known as the \emph{Lyapunov's form of the CLT}, employs the Lindeberg's method of replacement trick, Taylor expansion, and Big-O reasoning. Unlike earlier approaches that assume identical distributions, our formalisation accommodates inhomogeneous sequences, which introduces substantial technical overhead--particularly in bound variables--specific replacement errors. However, this effort yields a more widely applicable theorem under Lyapunov’s condition.

>>>>

To the best of our knowledge, this is the first mechanised proof of CLT beyond the I.I.D.~cases.
This version, usually known as the \emph{Lyapunov's form of the CLT}, employs the Lindeberg's method of replacement trick, Taylor expansion, and Big-O reasoning. Unlike earlier approaches that assume identical distributions, our formalisation accommodates inhomogeneous sequences, which introduces substantial technical overhead--particularly in bounding variables--specific replacement errors. However, this effort yields a more widely applicable theorem under Lyapunov’s condition.
